
\documentclass[margin, 10pt]{res}
    \usepackage{helvet} % Default font is the helvetica postscript font
    %\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
    
    \setlength{\textwidth}{5.1in} % Text width of the document
    
    \begin{document}
    
    %----------------------------------------------------------------------------------------
    %	NAME AND ADDRESS SECTION
    %----------------------------------------------------------------------------------------
    
    \moveleft.5\hoffset\centerline{\large\bf Aniket Sharma} % Your name at the top
     
    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
     
    \moveleft.5\hoffset\centerline{Site: http://aniket965.ml} % Your address
    \moveleft.5\hoffset\centerline{New Delhi, India - 110052}
    \moveleft.5\hoffset\centerline{Phone No. : +91 9899023974}
    \moveleft.5\hoffset\centerline{Email : aniket965.as@gmail.com}
    %----------------------------------------------------------------------------------------
    
    \begin{resume}
    
    %----------------------------------------------------------------------------------------
    %	Interests
    %----------------------------------------------------------------------------------------
     
    \section{INTERESTS}  
    
    Software Development,Web Assembly, Deep Learning, Computer Vision, Artificial Intelligence, Image/Video Processing, Product Designing
    
    %----------------------------------------------------------------------------------------
    %	Training and Internships 
    %----------------------------------------------------------------------------------------
    
    \section{INTERNSHIPS}
    
    {\sl \bf{Intern at Erp Cell for Eventinta Project }}\null\hfill Jun. 2018-Aug. 2018\\
    Led by : Dr. Manoj Sharma (Associate Professor, Dept of ECE). 
    
    %----------------------------------------------------------------------------------------
    %	Technical Skills 
    %----------------------------------------------------------------------------------------
    
    \section{TECHNICAL \\ SKILLS} 
    
    {\sl Programming Languages:} Swift, TypeScript, Processing, Kotlin, Ardiuno, Shell, C\#, Java, Javascript, Python, C, Embedded C, MATLAB, LaTex. \\
    {\sl Design Languages:} HTML, CSS, SCSS, Jade \\
    {\sl Embedded Platforms:} Raspberry Pi, Arduino, Spark V,Pluto Drone\\
    {\sl Softwares and Libraries:} Flutter,VREP,Electron, Flask, Node.js,Vue, Redux, D3.js, Express, Mongo DB, Webpack, Git, OpenCV, TensorFlow, Blender (GUI and Scripting), Reactjs, React Native, Keras, tf.js, Jupyter Notebook, Unity, Sketch, Flask, Adobe XD, Android, IOS development, Playground Development. 
    
    
    %----------------------------------------------------------------------------------------
    %	Awards 
    %----------------------------------------------------------------------------------------
    
    \section{AWARDS \& HONORS}
    - {\sl {\bf Ranked \#1 in India} in overall contributions in opensource at Github}.\\
    - {\sl 3rd position at Dishathon 2018}.\\
    - {\sl Winner of IndiaHacks 2017 in Artificial Intelligence Theme}.\\
    - {\sl Winner of ClashHacks 3.0 }\\
    - {\sl Winner of Random Hack of kindness 2017 New Delhi}.\\
    - {\sl Winner of Ultrahack 2017 New Delhi}.\\
    - {\sl Winner of 3pillar global hackathon 2017}.\\    
     %----------------------------------------------------------------------------------------
    %	Education 
    %----------------------------------------------------------------------------------------
    \section{EDUCATION} 
    {\sl \bf{Bharati Vidyapeeth's College of Engineering}} \hfill 2016-2020(anticipated)\\ Bachelor of Technology in Electronics and Communication\\
    Current CGPA Score - 8.4/10.0
    
    {\sl \bf{Kendriya Vidyalaya Keshav Puram, Delhi}}
    \hfill 2014-2016 \\Higher Secondary Education\\ 88.89\% in AISSCE 2016
    
    {\sl \bf{Kendriya Vidyalaya Keshav Puram, Delhi}}\\High School(Class 10)\\CGPA 9.8 in CBSE Board Examination 2014
    
    \section{WORK EXPERIENCE}
    {\sl {\bf Software Developer and Devops Engineer }}\hfill Dec .2017-present \\
    Erp Cell, Bharati Vidyapeeth's College of Engineering, New Delhi.\\
    {\sl {\bf Software Developer }}\hfill Sept.2018-present \\
    Computer Cell DCP North Office , Delhi Police.\\
    {\sl {\bf Open Source Software Developer }}\hfill Sept.2016-present \\
    Created more than 100 packages and contributed to Apple Inc, Opencv, Openmind, Fossasia.\\
  
    
      \newpage

    % \vspace{-2.5 mm}
    
    % A vehicle-pedestrian and vehicle-vehicle collision alert system prototyped on Raspberry Pi alongside a smartphone application to infer speed and position data of vehicles as well as provide alerts.
    
    \section{PROJECTS}
    - {\bf Erp portal }\\
    A PWA for teachers of Bharati Vidyapeeth's College of Engineering including many Features to help them solving daliy tasks.
    
    - {\bf EventInsta }\\
    An open source PWA to notify people about various events and meetups in their preferred groups. This is created to target groups and chapters in my campus and other campuses to connect students and keep them updated with latest events.  
    
    - {\bf Collector Bot eYRC 2017} \\
    - Bot for Collecting  fine fruits from ground and and droping into a truck. Prototyped on Spark V 
    
    - {\bf Distro Music} \\ Distro music is PWA in which we can play music on the various connected device over a network, any device can load music and it will be uploaded to the server so that  every connected device can play it simultaneously. 
    
    - {\bf Eternal Flame}\\
    A Swift Package for creating animations in terminal by giving frames and type of easing in two line of code.
    %- {\bf Gaming Arcade using cost effective Pressure Sensors for feedback
    
    %----------------------------------------------------------------------------------------
    %	Leadership Experiences 
    %----------------------------------------------------------------------------------------
    
    \section{LEADERSHIP EXPERIENCE}
    {\sl {\bf Core  Member}}\hfill Dec. 2018-present \\
    IIC BVCOE (Sponsored by MHRD),New Delhi.\\ 
    {\sl {\bf Vice Chairperson}}\hfill Aug. 2017-present \\
     Intel AI Society, Delhi.\\
    {\sl {\bf Vice Chairperson}}\hfill Jun. 2017-Aug. 2018 \\
     Bvp Mozzila Student campus club,New Delhi.\\ 
    {\sl {\bf Core Team Member}}\hfill Jun. 2017-Dec. 2018 \\
     Microsoft User Group,New Delhi.\\ 
    

    %----------------------------------------------------------------------------------------
    %	Hobbies
    %----------------------------------------------------------------------------------------
    
    \section{HOBBIES}
    I seek pleasure in creating anything that can help others. The idea of sharing stories through just pictures amuses me, hence my love for photography. I relish solitude as much as I like talking to people and most of my conversations generally begin with or include music apart from talks about science, upcoming trends in technology or interesting things that I come across on the Internet.
    \\

    \section{}
    I hereby declare that above-mentioned information is correct to the best of my knowledge and belief.\\

    {\bf Place}: New Delhi\\
    {\bf Date}:27 JAN 2019 \null\hfill {\bf Signature}\\
    \end{resume}
    \end{document}